The \project{unRAVE} catalog

### 2016-09-07 article/unrave.tex
Updated text in gold standard comparison, since MP dwarf/subgiant issue now fixed

We searched the literature for studies that overlap with \rave, and which base
their analysis on high-resolution, high S/N spectra.  We found four notable
studies with a sufficient level of overlap: the disk studies by \citet{Reddy_2003,Reddy_2006}
and \citet{Bensby_2014}, as well as the \citet{Valenti_Fischer_2005} work on exoplanet
host star candidates.  These studies 
perform a careful (manual; expert) analysis using extremely high-resolution

, high S/N spectra, and make use of \project{Hipparcos}
parallaxes where possible.  Most of the stars in these samples are main-sequence
or sub-giant stars.  Therefore, these works constitute an excellent comparison
to evaluate the accuracy of our results on the main-sequence and sub-giant branch.

We compare the stellar parameters ($\teff$, $\logg$, [Fe/H]) of stars that
overlap these literature studies in Figure~\ref{fig:gold-standard-comparison}.
We only include stars with $\chi_r^2 < 3$ and $S/N > 10$~pixel$^{-1}$, although the latter
cut removed only few stars because the average S/N in the \rave\ spectra for
these stars is relatively high ($\gtrsim{}50$~pixel$^{-1}$). When considering the relative 
information content available in \rave\ (945~pixels in the near infrared with
$\mathcal{R} \approx 7{,}500$) compared to these literature studies (\stub{what snr, resolution, wavelength range and hipparcos parallaxes}, we consider the
 agreement to be satisfactory.

There are some discrepancies between our results and these literature studies,
and these differences arise from the manner in which we join results from the
main-sequence and giant model.  Specifically, for metal-poor stars near
the turn-off in these literature comparisons, in our weighted results we find 
these stars to have similar metallicities, but to be slightly more evolved: 
on the sub-giant branch or the base of the giant branch.  This effect is best
illustrated in Figure~\ref{fig:gold-standard-hrd}, where we show a 
Hertzsprung-Russell diagram for all stars in common between this work and that
of \citet{Bensby_2014,Reddy_2003,Reddy_2006,Valenti_Fischer_2005}.  While the
overall shape of the turn-off in our work is consistent with the literature
studies (right panel), the linked data points in the first three panels show that metal-poor stars in the literature
appear as more evolved stars in our combined results.  Instead, if we only
take the results from our main-sequence model --- ignoring the influence of the
giant model --- and compare those values to these literature studies, no such 
systematic discrepancies are present in the Hertzsprung-Russell diagram: we 
find those metal-poor turn-off stars to also be turn-off stars, with comparable
metallicities.  Our investigation indicates that this issue affects dwarf stars
near the turn-off that have $[{\rm Fe/H}] \lesssim -1$.  While the agreement
would improve if we adopted the main-sequence results for these specific stars,
the underlying issue of metal-poor dwarf stars would still be present.  Thus,
we use this example to illustrate caution for studies making inferences from our
work based on main-sequence dwarf stars.  The results from both the main-sequence star model, 
and the giant star model, are available on request. \stub{should we put them online somewhere
for open-science, or just make them available upon request so that we don't
muddy the waters and confuse people as to which catalog to use?}

We note that this issue does not appear to affect our derived metallicities for these
stars.  For this reason, if stars affected by this issue can be confirmed to be
dwarfs by external information --- rather than being sub-giants as our analysis
suggests for some --- then the metallicity we report can still be considered
useful.  For the more metal-rich dwarf stars, the sample we present here
will undoubtedly be informative for upcoming studies based on exoplanet host
star properties.  At present, however, there are just $\approx$30 stars in 
\rave\ that overlap with the compilations of exoplanet host star properties 
listed at \texttt{exoplanets.org} and \texttt{exoplanets.eu}.

>>>>

We searched the literature for studies that overlap with \rave, and which base
their analysis on high-resolution, high S/N spectra.  We found four notable
studies with a sufficient level of overlap: the disk studies by \citet{Reddy_2003,Reddy_2006}
and \citet{Bensby_2014}, as well as the \citet{Valenti_Fischer_2005} work on exoplanet
host star candidates.  These studies 
perform a careful (manual; expert) analysis using extremely high-resolution, high S/N spectra, and make use of \project{Hipparcos}
parallaxes where possible.  Most of the stars in these samples are main-sequence
or sub-giant stars.  Therefore, these works constitute an excellent comparison
to evaluate the accuracy of our results on the main-sequence and sub-giant branch.

We compare the stellar parameters ($\teff$, $\logg$, [Fe/H]) of stars that
overlap these literature studies in Figure~\ref{fig:gold-standard-comparison}.
We only include stars with $\chi_r^2 < 3$ and $S/N > 10$~pixel$^{-1}$, although the latter
cut removed only few stars because the average S/N in the \rave\ spectra for
these stars is relatively high ($\gtrsim{}50$~pixel$^{-1}$). When considering the relative 
information content available in \rave\ (945~pixels in the near infrared with
$\mathcal{R} \approx 7{,}500$) compared to these literature studies that use
\project{Hipparcos} parallaxes where possible, and base their inferences on
spectra with resolving power $\mathcal{R}$ between 40,000 to 110,000, and
S/N ratios exceeding 150, we consider the agreement to be very satisfactory.
Indeed, given the metallicity precision available in the \unrave\ catalog, 
these results will likely be useful for future studies based on exoplanet
host star properties (e.g., \project{TESS}). At present, however, there are 
just $\approx$30 stars in \rave\ that overlap with the compilations of 
exoplanet host star properties listed at \texttt{exoplanets.org} and 
\texttt{exoplanets.eu}.
